Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-16 manuscript.Rnw
Download BAAD database

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
source("R/functions-ms.R")
baad <- readRDS("data/baad.rds")
dataauthors <- author_details(baad, "data/contact.csv")
@

>>>>

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
source("R/functions-ms.R")
baad <- readRDS("downloads/baad.rds")
dataauthors <- author_details(baad, "data/contact.csv")
@
